---
title: "Poweranalyse"
subtitle: "Zero-One Inflated Regression"
author: "Samuel Merk, Sarah Bez, Martin Tomasik"
date: "`r Sys.Date()`"
output: tint::tintPdf
link-citations: yes
---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
```

# Defining the population effect
As a first step we define the population according to the findings from Study 1.
```{r, message=FALSE}
library(bayestestR)
library(tidyverse)
library(hrbrthemes)

# setting seed for reproducibility
set.seed(9174)

data_heatmap <- 
  c(distribution_beta(203, 4.5, 3),
    rep(0, 5), rep(1,5))

data_table <- 
  c(distribution_beta(203, 3, 3.5),
    rep(0, 8), rep(1,2))

data <- 
  tibble(
    ari = c(data_heatmap,
             data_table),
    group = c(
      rep("heatmap", 213),
      rep("table", 213)
    ))
```


```{r, fig.margin=TRUE, fig.width=4, fig.height=4, message = F, results = 'hide', warning=FALSE, echo=FALSE}
ggplot(
  data, aes(ari)) +
  geom_histogram() +
  facet_wrap( ~ group, ncol = 1) +
  theme_minimal()
```

The effect size for this data is as follows: 

```{r}
effsize::VD.A(data_table, data_heatmap)
```

# Sampling & Estimation
```{r, results = "hide"}
# Initialize a vector of results
CI_with_zero <- logical()

# setting seed for reproducibility
set.seed(8742)

length_sim <- 1

for (i in 1:length_sim){
# Sampling
data_sampled <- 
  data %>% 
  group_by(group) %>% 
  sample_n(100)

# Fitting the model
library(brms)
fit <- brm(
  formula = bf(
    ari ~ 1 + group),
  data = data_sampled,
  silent = 0,
  family = zero_one_inflated_beta())

fit_summary <- 
  summary(fit)

# Storing the result
CI_with_zero[i] <- 
  sign(fit_summary$fixed$`l-95% CI`[2]) != 
  sign(fit_summary$fixed$`u-95% CI`[2])
}
```

# Power of the Model
Despite the fact that "power" is a somewhat awkward entity within a Bayesian framework, we use it here to describe the proportion of simulated data sets which to not contain the zero in its highest density interval. This proportion equals:

```{r}
1 - sum(CI_with_zero)/length_sim |> 
  round(2)
```
